Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-28 paper/paper-mainfile.tex

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration. This is when it's configured to turn the problem into a classical planning problem (in RC model), and Greedy best first search, using FF by \cite{FF}, and using visited lists. The visited lists use task sequence hashing, visited checking with task sequences which makes totally-ordered visited lists incomplete (with order), layer hashing, order pairs hashing, no optimisation for parallel sequences,  GI-complete equivalence checking for
partially ordered task networks (with GI-complete checking).

@@

>>>>

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration. This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists. The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.

% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)

@@

While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
\begin{table} 
	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain. Shows Results for Both Inference Methods.}\label{} 
	\begin{tabular}{lccl} 
		\toprule 
		Domain & Complex & Simple &  \\ 
		\midrule
		Transport & 1.0 & 0.0  \\ 
		UM-Translog & 0.8 & 0.0  \\ 
		Satellite & 1.0 & 0.0  \\ 
		Monroe Fully Observ. & 1.0 & 0.0  \\ 
		Rover & 1.0 & 0.0  \\ 
		Woodworking & 0.9 & 0.0  \\ 
		Monroe Part. Observ. & 1.0 & 0.0  \\ 
		PCP & 0.0 & 0.0  \\ 
		Barman-BDI & 1.0 & 0.0  \\ 
		SmartPhone & 0.1 & 0.1  \\ 
		Monroe & 0.8 & 0.0  \\ 
		Zenotravel & 1.0 & 0.0  \\ 
		\bottomrule 
	\end{tabular} 
\end{table}
